Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Cambiada estructura de algunos párrafos para leerlo más fácil, hyphenation y otros comentarios en la Introducción y abstract

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and their Chief Security Officers (CSOs) particularly, want to be sure that their Security Policies are complied. This goal turned hard to achieve since employees are able to use their own devices (laptops, smartphones, and tablets) at work, or at home but for work purposes. As this is part of the Bring Your Own Device (BYOD) philosophy and is being adopted by many companies everyday, a number of solutions have arisen in order to adapt it securely. In this paper, a novel system to deal with this situation is introduced, named  MUSES (Multiplatform Usable Endpoint Security). It is a system able to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules. MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
This system, still in development, is compared with the most relevant solutions offered by other companies to deal with the same issues as MUSES, remarking the advantages that our system will offer with respect to them.
\end{abstract}

@@

The way on how data has been stored and accessed in the companies has completely changed along the years. The use of owned servers being accessed by desktop PCs (and maybe laptops) from inside the company facilities has been transformed into the distribution of these data between a number of machines, even not all belonging to the company, and working over the famous Cloud Computing environment. Besides, being stored in the cloud or not, data are being consulted and modified through a wide amount of devices, some of them owned by the company's users. This is the so-called Bring Your Own Device (BYOD) philosophy. It is becoming highly successful due to the impact that portable devices (such as smartphones and tablets) are having on the market.
Data security and privacy are key factors for a company, thus, to protect them, it is usual to define Organisational Security Policies. Their definition is nowadays a very difficult problem, since the BYOD tendency means that several factors must be considered \cite{Opp_Security11}, most of them previously ignored or non considered in security systems, for instance the current mixture between personal and professional information in these devices (the user could navigate inside social networks where there could be friends and also company partners or clients).

@@

Thus, this work introduces a novel (still in development) system named MUSES, from Multiplatform Usable Endpoint Security, which is a device-independent end-to end user-centric tool, based on a set of security rules defined as specifications of the Corporate Security Policies, but with the ability of `learning' from the user's past behaviour and adapt, even inferring new ones, the set of rules in order to deal with potential future security incidents due to the user's. Then the system will react, in a non-intrusive way, to the potentially dangerous sequence of actions (events) that he or she is conducting at any time.

@@

MUSES will include some important modules in the loop, such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them and extracting threads that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset.

In the paper the system architecture is presented, in addition to a deep description of the soft computing methods the system will apply.

>>>>

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and their Chief Security Officers (CSOs) particularly, want to be sure that their Security Policies are complied. This goal turned hard to achieve since employees are able to use their own devices (laptops, smartphones, and tablets) at work, or at home but for work purposes. As this is part of the Bring Your Own Device (BYOD) philosophy and is being adopted by many companies everyday, a number of solutions have arisen in order to adapt it securely. In this paper, a novel system to deal with this situation is introduced, named  MUSES (Multiplatform Usable Endpoint Security). This system is able to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules. MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
This system, still in development, is compared with the most relevant solutions offered by other companies to deal with the same issues as MUSES, remarking the advantages that our system will offer with respect to them.
\end{abstract}

%FERGU: seguro que ya lo habéis discutido, pero presentar MUSES como algo a hacer en el futuro es un poco... yasabesh xD

@@

The way on how data has been stored and accessed in the companies has completely changed along the years. The use of owned servers being accessed by desktop PCs (and maybe laptops) from inside the company facilities has been transformed into the distribution of these data between a number of machines, even not all belonging to the company, and working over the famous Cloud Computing environment. Besides, being stored in the cloud or not, data are being consulted and modified through a wide amount of devices, some of them owned by the company's users. This is the so-called Bring Your Own Device (BYOD) philosophy. It is becoming highly successful due to the impact that portable devices (such as smartphones and tablets) are having on the market.
Data security and privacy are key factors for a company, thus, to protect them, it is usual to define Organisational Security Policies. Their definition is nowadays a very difficult problem, since the BYOD tendency means that several factors must be considered \cite{Opp_Security11}, most of them previously ignored or non considered in security systems. For instance, the current mixture between personal and professional information in these devices (the user could navigate inside social networks where there could be friends and also company partners or clients).

@@

Thus, this work introduces a novel (still in development) system named MUSES, from Multiplatform Usable Endpoint Security, which is a dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a set of security rules defined as specifications of the Corporate Security Policies, but with the ability of `learning' from the user's past behaviour and adapt the set of rules, or even inferring new ones, in order to deal with potential future security incidents due to the user's. %FERGU: The user's "algo que falta"? o eso hace referencia a su culpa?
Then the system will react, in a non-intrusive way, to the potentially dangerous sequence of actions (events) that he or she is conducting at any time.

@@

MUSES will include some important modules in the loop, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
 such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them and extracting threads that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset.

In this paper, the system architecture is presented, in addition to a deep description of the soft computing methods the system will apply.
